---
title: "EDA"
author: "SDLG"
date: "2/25/2022"
output: 
  html_document:
    keep_md: true
---
Taking a look at the dataset
```{r}
billionaire.data = read.csv("C:\\Users\\Servando\\Downloads\\archive (34)\\Billionaire.csv")
head(billionaire.data)
```
Checking for type errors and fixing them with casting.(Data Cleaning)


```{r}
require("readr")
#Checking types
typeof(billionaire.data$NetWorth)
typeof(billionaire.data$Age)
#Changing types to appropiate ones
billionaire.data$NetWorth <- as.numeric(parse_number(billionaire.data$NetWorth))
billionaire.data$Age <- as.numeric(billionaire.data$Age)
#Changing column name
colnames(billionaire.data)[2]<-"Net_Worth_Billions"
#Checking dataframe
head(billionaire.data)
```
How does the five number summary look like for net worth? What’s the standard deviation?


```{r}
summary(billionaire.data$Net_Worth_Billions)
sd(na.omit(billionaire.data$Net_Worth_Billions))
```
Let’s figure out how the distribution looks like.
```{r}
require("ggplot2")
require("moments")
Networth_billions <- billionaire.data$Net_Worth_Billions
skewness(billionaire.data$Net_Worth_Billions)

ggplot ( data = billionaire.data)+geom_histogram(mapping = aes(x =Net_Worth_Billions ),binwidth = 0.5,color = "darkgreen")+ggtitle("Net Worth Frequency Distribution")

```
What’s the number of billionaires per industry?
```{r}
require("dplyr")
require("wesanderson")
by.industry <- billionaire.data %>%
group_by(Industry) %>%
summarise(number.of.billionaires <- n()
)

by.industry$Industry<- factor(by.industry$Industry,levels = by.industry$Industry[order(by.industry$`number.of.billionaires <- n()`)])
par(mar=c(19,4,4,1))
industry.plot <- ggplot(data = by.industry, aes(x = Industry, y =`number.of.billionaires <- n()` , fill =Industry ))+ geom_bar(stat = "identity") +ggtitle("Number of Billionaires by Industry") +
  geom_text(aes(label =`number.of.billionaires <- n()` ), hjust =1 ,color = "white", size = 3.5)+
  theme_minimal()+coord_flip() 
industry.plot + theme_bw() 

  
```

Now, let’s break it down by country.
```{r}
by.country <- billionaire.data %>%
group_by(Country) %>%
summarise(number.of.billionaires <- n()
)
by.country <- by.country[order(-by.country$`number.of.billionaires <- n()`),]
colnames(by.country)[2]<-"Number of Billionaires"
top<- top_n(by.country,5)
top$Country<- factor(top$Country,levels = top$Country[order(top$`Number of Billionaires`)])
group.colors <-c(`United States` = "darkblue", China="Darkred",India = "Orange",Germany="Darkgreen",Russia = "purple")
ggplot(data = top, aes(x = Country, y =`Number of Billionaires`,fill = Country ))+
  geom_bar(stat = "identity")+ coord_flip() +ggtitle("Top 5 Countries with Most Billionaires") +
  geom_text(aes(label = `Number of Billionaires`), hjust = -.1 , size = 3.5)+
  theme_minimal() + scale_fill_manual(values=group.colors)

```

Let’s check for a correlation between age and NetWorth.
```{r}
require("ggplot2")
par(mar=c(10,6,6,1))
ggplot(billionaire.data) + geom_point(mapping = aes(x = Age , y = Net_Worth_Billions ,color=Industry))+
  ggtitle("Correlation Between Net Worth and Age by Industry")
```
Let’s look at the five number summary of the billionaires’ age.
```{r}
summary(billionaire.data$Age)
```
Now, Let's compare the age of billionaires of the 5 industries with most billionaires
```{r}

five.industries <- billionaire.data %>% filter(Industry == c("Finance & Investments","Technology","Manufacturing","Fashion & Retail","Healthcare"))

agesplot <- ggplot(data = five.industries , mapping = aes(x=reorder(Industry,Age,FUN=median), y = Age, fill = Industry)) +
  geom_boxplot() +
  coord_flip()

agesplot
```
Now, let's see how that comparison it's like for net worth
```{r}
ggplot(data = five.industries , mapping = aes(x=reorder(Industry,Net_Worth_Billions,FUN=median), y = Net_Worth_Billions, fill = Industry)) +
  geom_boxplot() +
  coord_flip()
```

